---
title: "HW03"
author: "Victor Majestic"
date: "11/11/22"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

### 1a.i

```{r}
p0 = (4.5^0*exp(-4.5))/factorial(0)
p1 = (4.5^1*exp(-4.5))/factorial(1)
p2 = (4.5^2*exp(-4.5))/factorial(2)
p3 = (4.5^3*exp(-4.5))/factorial(3)
p0 + p1 + p2 + p3
```

### 1a.ii
```{r}
ppois(3, 4.5, lower.tail = TRUE)
```

### 1b.i
```{r}
p4 = (4.5^4*exp(-4.5))/factorial(4)
p5 = (4.5^5*exp(-4.5))/factorial(5)
p6 = (4.5^6*exp(-4.5))/factorial(6)
p3 + p4 + p5 + p6
```

### 1b.ii
```{r}
ppois(6, 4.5, lower.tail = TRUE) - ppois(2, 4.5, lower.tail = TRUE)
```

## Question 2

### 2a
```{r}
pnorm(6.3, 5, 3, lower.tail = TRUE, log.p = FALSE)
```

### 2b
```{r}
pnorm(7.8, 5, 3, lower.tail = FALSE, log.p = FALSE)
```

### 2c
```{r}
pnorm(7.8, 5, 3, lower.tail = TRUE, log.p = FALSE) - pnorm(1.6, 5, 3, lower.tail = TRUE, log.p = FALSE)
```

### 2d
```{r}
qnorm(0.95, 5, 3, lower.tail = TRUE)
```

### 2e
```{r}
lowerbound = qnorm(0.025, 5, 3, lower.tail = TRUE)
-lowerbound + 5
```

## Question 3

### 3a
```{r}
set.seed(101)
sample = rnorm(10000, 7, 2)
mean(sample)
sd(sample)
```

### 3b
```{r sample}
hist(sample)
```

## Question 6.1.12

### 6.1.12a
```{r}
Rainfall <- read.csv("Ex6_1_12.csv", header=T)
mean(Rainfall$rainfall)
sd(Rainfall$rainfall)
range(Rainfall$rainfall)
max(Rainfall$rainfall) - min(Rainfall$rainfall)
```

### 6.1.12b
```{r}
Unseeded <- Rainfall[1:26, 1]
mean(Unseeded)
sd(Unseeded)
range(Unseeded)
max(Unseeded) - min(Unseeded)
```

### 6.1.12c
```{r}
Seeded <- Rainfall[27:52, 1]
mean(Seeded)
sd(Seeded)
range(Seeded)
max(Seeded) - min(Seeded)
```

## Question 6.2.4

```{r}
Gasoline <- read.csv("Ex6_2_4.csv", header=T)
stem(Gasoline$OctRating)
quantile(Gasoline$OctRating, probs = c(0, 0.25, 0.5, 0.75, 1))

```

## Question 6.4.9
```{r}
Drug <- read.csv("Ex6_4_9.csv", header = T)
HighDose <- Drug[1:21, 1]
Control <- Drug[22:82, 1]
boxplot(HighDose)
boxplot(Control)
```
Neither distribution follows a normal curve. Both distributions are right-skewed, with the control group being an almost extreme case. The high-dose distribution has a median between 40 and 60. 25% of gene activity values fall between roughly 75 and the maximum 134.9; meanwhile the lower 75% fall within a similar range of the minimum 12.9 and roughly 75. The control group is even more right-skewed; 50% of the data values are greater than roughly 330. The maximum is around 3000. It appears as if this distribution has 7 extreme outliers. It is also evident that the median (and basically all of the distribution) of the high-dose group is much lower than that of the control group, indicating that the high-dose is effective in lowering gene activity.
